### 2020-01-18 all_models.tex
added prelim all models tex

>>>>

\charlesx{We actually don't run regressions on all these datasetsm, BUT we could present them in the Figure below to show that alpha is a good metric for these kinds of models, in contrast to the NLP, where alpha is frequently too large to run a regression}

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=4cm]{img/imagenet1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=4cm]{img/cifar10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=4cm]{img/cifar100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=4cm]{img/svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=4cm]{img/cub200_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{\charles{Preliminary charts:} Heavy Tailed Power Law exponent $\alpha$ vs. reported Top1 Test Accuracies for pretrained DNNs available\charles{ref} for 5 different data sets.}

    \label{fig:dataset_alphas}
\end{figure}
